### 2013-06-23 trunk/network-science/paper.tex
8

\subsection{Desiderata}
Suppose $Act(G_t,v)$ returns the activity of node $v$ in the evolving graph in
time $t$. Then $Act(G_t,v)$ should be a deterministic function of $v$ and
$E_t$.
\begin{itemize}
\item \textbf{normalization}:

@@

\begin{equation}

\end{equation}

\end{itemize}
\subsection{Design and Analysis}
% TODO
\section{Algorithms}
% TODO
\subsection{Maintaining the basic graph structure}
% TODO
\subsection{Historical Queries}
% TODO
\subsection{Computing Metrics}
% TODO
\subsection{Mining Significant Data}
% TODO
\subsection{Optimization and Parallelizability}
% TODO
\section{Experiment}
% TODO
\section{Conclusion and Perspective}
% TODO
\nocite{*}
\bibliography{paper.bib}
\end{document}

>>>>

\subsection{Desiderata}
\definition $Act(G_t,v)$ returns the activity of node $v$ in the evolving graph in
time $t$. Then $Act(G_t,v)$ should be a deterministic function of $v$ and
$E_t$.
\begin{itemize}
\item \textbf{normalization}:

@@

\begin{equation}
todo
\end{equation}

\end{itemize}
\subsection{Design and Analysis}
% TODO
\section{Algorithms}
% TODO
\subsection{Maintaining the basic graph structure}
% TODO
\subsection{Historical Queries}
% TODO
\subsection{Computing Metrics}
% TODO
\subsection{Mining Significant Data}
% TODO
\subsection{Optimization and Parallelizability}
% TODO
\section{Experiment}

We have implemented two of the algorithms using C++ language.
The program maintains a dynamic graph which contains $n$ vertices and does not have
any edge at the beginning.
It support the following operations:
\begin{itemize}
	\item \textsc{Add $u,v$:} increase the time counter by one, and then add an edge
		between vertex $u$ and vertex $v$.
	\item \textsc{QueryDeg $t,u$:} ask for the degree of $u$ at time $t$.
	\item \textsc{QueryCon $t,u,v$:} ask that whether vertices $u,v$ is connected or not
		$u$ at time $t$.
\end{itemize}
Note that the time counter is initially zero.
Each operation cost $O(\log n)$ time in our implemented algorithm.

\subsection{Checking for Correctness}
We implemented a simple algorithm together which cost $O(\max\{n,m\})$ time for each operation,
	where $m$ is the number of edges before the operation.
We have generated several small test cases and compare the results between the simple program
	and our $O(\log n)$ program.
There is no difference found between outputs of the two programs.

\subsection{Checking for Time Complexity}
We have generated several huge test cases to test the running time of the program.
The following tabular shows the informations about the cases and the running results.
\begin{center} \begin{tabular}{|c|c|c|c|c|}
	\hline
	Case & Number of & Number of & Density of & Running \\
	ID & vertices & operations & query & time \\
	\hline
	1 & 100000 & 200000 & 0.5 & 0.504 \\
	\hline
	2 & 100000 & 200000 & 0.5 & 0.524 \\
	\hline
	3 & 100000 & 200000 & 0.5 & 0.516 \\
	\hline
	4 & 200000 & 400000 & 0.5 & 1.072 \\
	\hline
	5 & 200000 & 400000 & 0.5 & 1.092 \\
	\hline
	6 & 200000 & 400000 & 0.5 & 1.072 \\
	\hline
	7 & 500000 & 500000 & 0.5 & 1.464 \\
	\hline
	8 & 500000 & 500000 & 0.5 & 1.492 \\
	\hline
	9 & 500000 & 1000000 & 0.5 & 2.772 \\
	\hline
	10 & 500000 & 1000000 & 0.5 & 2.732 \\
	\hline
	11 & 500000 & 2000000 & 0.5 & 5.232 \\
	\hline
	12 & 500000 & 2000000 & 0.5 & 5.256 \\
	\hline
	13 & 1000000 & 2000000 & 0.5 & 5.652 \\
	\hline
	14 & 1000000 & 2000000 & 0.5 & 5.808 \\
	\hline
	15 & 1000000 & 3000000 & 0.5 & 8.417 \\
	\hline
\end{tabular} \end{center}
We can see that the running time grows as linear as number of operations,
	but grows much slower when number of vertices grows (as $\log$).

\section{Conclusion and Perspective}
% TODO
\nocite{*}
\bibliography{paper.bib}
\end{document}
